Maps for translocation paper

### 2023-05-17 code/maps.qmd
Increase symbol and text size

```{r}
library(sf)
library(tmap)
library(stars)
library(grid)
library(readr)
```

## Map of exome capture sample sites

@@

```{r}
translocation_points_map <- tm_shape(hillshade_yose_crop) + 
  tm_rgb(r = 1, g = 2, b = 3) +
  tm_shape(yose_boundary) + 
  tm_borders(col = "black", lwd = 2) +
  tm_shape(translocation_points) + 
  tm_symbols(size = 0.7, 
             shape = "donor_id",
             col = "type", 
             legend.shape.show = FALSE, 
             palette = c("#0000FF", "#C0FF3E"), # tmap only recognizes basic color names (e.g., "blue" but not "lightblue") - use HEX instead
             title.col = "Population type") +
  tm_layout(legend.position = c("right", "top"),
            legend.bg.color = "white",
            legend.title.size = 1.3,
            legend.text.size = 1.0) +
  tm_compass(type = "4star",
             position = c(0.80, 0.11),
             size = 3) +
  tm_scale_bar(breaks = c(0, 10, 20), 
               text.size = 1.0, 
               position = c("right", "bottom"))

>>>>

```{r}
library(sf)
library(tmap)
library(stars)
library(grid)
library(tidyverse)
library(RPostgreSQL)
```

## Map of sample sites for exome capture analysis

@@

```{r}
translocation_points_map <- tm_shape(hillshade_yose_crop) + 
  tm_rgb(r = 1, g = 2, b = 3) +
  tm_shape(yose_boundary) + 
  tm_borders(col = "black", lwd = 2) +
  tm_shape(translocation_points) + 
  tm_symbols(size = 0.9, 
             shape = "donor_id",
             col = "type", 
             legend.shape.show = FALSE, 
             palette = c("#0000FF", "#C0FF3E"), # tmap only recognizes basic color names (e.g., "blue" but not "lightblue") - use HEX instead
             title.col = "Population type") +
  tm_layout(legend.position = c("right", "top"),
            legend.bg.color = "white",
            legend.title.size = 1.5,
            legend.text.size = 1.2) +
  tm_compass(type = "4star",
             position = c(0.80, 0.11),
             size = 5) +
  tm_scale_bar(breaks = c(0, 10, 20), 
               text.size = 1.2, 
               position = c("right", "bottom"))
